\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Milav Dabgar} \\
\indent 1-k-86, \\
\indent Vivekanannd Nagar,  \\
\indent Ahmedabad (Gujarat, INDIA) - 382445\\
\indent Email-id : \textbf{milav.dabgar@gmail.com} \\
\indent Mobile No.: \textbf{8128576285} \\
\indent Alt Mob No.: \textbf{9426676285} \\

\resheading{\textbf{EXPERIENCE} }\\[\lsep]
\begin{itemize}
\item \textbf{Lecturer - Class2} (Nov'16 - Present) \\
 \emph{(Government Polytechnic (Education Department - Government of Gujarat))} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item To Conduct Lab and Lecture Sessions for assigned courses. (Taken Courses Includes - Programming in C, Microprocessor and Assembly Language Programming, Micro controller, Embedded Systems, Circuit Design and Tools, Consumer Electronics, Entrepreneurship and Industrial Management etc. )
	\item To Serve as a Member/Convener of various College/University Level Portfolios. Currently Part of Following College Level Committees - DTE-MIS Committee, Campus Network Administration Committee, KCG Finishing School Programme Committee, SSIP - Students Startup and Innovation Policy Committee.
	\item To guide Students for Innovative Projects.
	\item To Serve as an academic adviser to the students.
\end{itemize}

\item \textbf{Electronics and Communication Engineer} (Jul'15 - Oct'16) \\
 \emph{(TEXEG India Private Limited)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Test Setup, Data Collection, Data Analysis and Reports generation of ongoing Projects.
	\item Designing and Tuning Controller (PID, PI, Fuzzy logic controller) using ‘Control System Toolbox -MATLAB’ and other related tools.
	\item Design, develop, code, test and debug system firmware.
	\item Design, develop, test, and troubleshooting system hardware.
	\item Providing complete embedded solution needed by all the ongoing Projects and product development.
	\item Providing electronics support to the Project Team (Mechanical) for ongoing Project Operations.This project was done as work for final year degree project.
	\end{itemize}
\end{itemize}

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{CPI/\%} \\
\hline
Post Graduate Specialization:\,\, & \textit{Communication Systems Engineering} \\
Post Graduation & GTU, Ahmedabad & LDCE, A'bad & 2015 & 8.04 \\
UnderGraduate Specialization: & \textit{Electronics and Communication Engineering} \\
Graduation & GTU, Ahmedabad & SALITER, A'bad & 2013 & 7.28\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Computers | Networks | Embedded | IOT | Linux | Python | R | Data | Pattern | CV| ML | DL | Music | Yoga
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} (C, C++, Python, Verilog, VHDL, Matlab, Python, Shell, R, \LaTeX), 
\item \noindent \textbf{CAD Tools} (OrCAD, eagle CAD, Altium Designer),
\item \noindent \textbf{Tools} (Matlab, Xilinx, Proteus, Multisim, OpenCV, Cisco Packet Tracer, GNS3, Wireshark, IntelliJ, Eclipse, VSCode, Keil, STM32Cube, MPLab, AVR Studio, Rstudio) 
\item \noindent \textbf{MCUs} (8051, ARM, Arduino, STM8, STM32, Raspberry Pi)
\item \noindent \textbf{OS} (DOS, MS Windows, Android, Linux - Arch Linux, Fedora, Debian, CentOS, OpenSUSE, Manjaro)
\end{itemize}

\resheading{\textbf{MAJOR PROJECTS AND SEMINAR} }\\[\lsep]
\begin{itemize}
\item \textbf{FPGA Implementation of Image Steganography} (Dissertation Project) \\
 \emph{(Guide:Prof. Priti Muliya and Ashish Purani, Jun'14 - Jun'15)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item In this work, we review recent developments in the field of steganography keeping real time covert communication applications in mind. We then propose a micro-architecture to transform the existing one of most successful Steganographic technique, Yet Another Steganographic Scheme (YASS) to the hardware platform for satisfying the current Steganographic application needs. This hardware will be able to resist the Self-calibration based blind Steganalysis attacks, which are the most successful attacks in breaking any Steganographic technique till now.
	\end{itemize}

\item \textbf{Wireless Data Acquisition System} (B.E. Project) \\
 \emph{(Guide: Prof. Shyamal Pampattivar, Jan'13 - Jun'13)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item This project was done as work for final year degree project.
	\end{itemize}
\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
\item \noindent Positive Attitude, Social Interaction, Hardworking.
\end{itemize}

\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Yoga - Practising and Teaching.
\item \noindent Blogging.

\end{itemize}

\end{document}